Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-27 ms.tex
cutting fat - and lots of it12

The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
time, $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$, for each accretion
rate shown in the top panel.  For SMBHs which accrete steadily at the
rate set by the stellar wind heating due to the average star formation
history of their host galaxies, we see that $t_{\rm grow}$ exceeds the
Hubble time by 1$-$3 orders of magnitude across all $M_{\bullet}$.
Steady accretion therefore cannot explain the growth of low mass black
holes, a fact which is not surprising given that approximately half of
this growth occurs in AGN radiating within 10 per cent of their
Eddington rate (\citealt{Heckman+04}).  Such high accretion rates
likely instead require an source of gas external to the nuclear
region, triggered either by galaxy mergers associated with the
hierarchical growth of structure or thermal instabilities on larger,
galactic scales (e.g.~\citealt{Ciotti+10}, \citealt{Voit+15}).  In
support of this, \citet{Kauffmann&Heckman09} find that the growth of
low mass black holes is dominated by young stellar bulges which have a
log normal distribution of Eddington ratios peaked at
$\Mdot/\dot{M}_{\rm edd} \sim 0.01$. That this distribution is
insensitive to galaxy properties suggests that it is set by SMBH
feedback instead of the nuclear gas supply.

@@

 We also note that \citet{Tchekhovskoy+2014} favor a smaller black hole
($10^5-10^6 \Msun$) for J1644+57 based on the observed jet power, the jet
shut-off time (if linked with the accretion becoming sub-Eddington), and an
observed QPO in the x-ray light curve favor a smaller black hole {\bf
  AG Gone mad!}.

@@

This prediction is also consistent with the observed dependence of
$\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
(Fig.~\ref{fig:miller}, green line), suggesting that accretion
regulation by kinetic feedback could play a role in determining the
X-ray luminosities of elliptical galaxies.  However, our assumption
that kinetic outflows heat the gas uniformly in volume is rather
arbitrary and would need to more rigorously justified by numerical
studies of how jets or disk outflows couple energy to their gaseous
environment.  As already discussed, it is furthermore unclear whether
a steady-state accretion model is at all relevant in the case when
SMBH feedback dominates due to the time delay between the small scale
accretion flow and the thermodynamic response of the CNM on larger
scales.

>>>>

The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
time, $t_{\rm grow} \equiv M_{\bullet}/\dot{M}_{\bullet}$, for each accretion
rate shown in the top panel, where we remind that $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha = 0.1$.  For SMBHs which accrete steadily at the
rate set by the stellar wind heating due to the average star formation
history of their host galaxies, we see that $t_{\rm grow}$ exceeds the
Hubble time by 2$-$4 orders of magnitude across all $M_{\bullet}$.
Steady accretion therefore cannot explain the growth of low mass black
holes, a fact which is not surprising given that approximately half of
this growth occurs in AGN radiating within 10 per cent of their
Eddington rate (\citealt{Heckman+04}).  Such high accretion rates
likely instead require an source of gas external to the nuclear
region, triggered either by galaxy mergers associated with the
hierarchical growth of structure or thermal instabilities on larger,
galactic scales (e.g.~\citealt{Ciotti+10}, \citealt{Voit+15}).  In
support of this, \citet{Kauffmann&Heckman09} find that the growth of
low mass black holes is dominated by young stellar bulges which have a
log normal distribution of Eddington ratios peaked at
$\Mdot/\dot{M}_{\rm edd} \sim 0.01$. That this distribution is
insensitive to galaxy properties suggests that it is set by SMBH
feedback instead of the nuclear gas supply.

@@

% We also note that \citet{Tchekhovskoy+2014} favor a smaller black hole
%($10^5-10^6 \Msun$) for J1644+57 based on the observed jet power, the jet
%shut-off time (if linked with the accretion becoming sub-Eddington), and an
%observed QPO in the x-ray light curve favor a smaller black hole {\bf
 % AG Gone mad!}.

@@

This prediction is also consistent with the observed downsizing trend of
$\langle L_{X}/L_{\rm edd} \rangle$ in elliptical galaxies
(Fig.~\ref{fig:miller}, green line), suggesting that accretion
regulation by kinetic feedback could play a role in determining the
X-ray luminosities of elliptical galaxies.  However, our assumption
that kinetic outflows heat the gas uniformly in volume is rather
arbitrary and would need to more rigorously justified by numerical
studies of how jets or disk outflows couple energy to their gaseous
environment.  As already discussed, it is furthermore unclear whether
a steady-state accretion model is at all relevant in the case when
SMBH feedback dominates due to the time delay between the small scale
accretion flow and the thermodynamic response of the CNM on larger
scales.
